Counterfactual Training: Teaching Models Plausible and Actionable Explanations

### 2025-03-15 paper/preprint/paper.tex
rerendered full file

In the natural language processing (NLP) domain, counterfactuals have
similarly been used to improve models through data augmentation. Wu et
al. (\citeproc{ref-wu2021polyjuice}{2021}) propose \emph{Polyjuice}, a
general-purpose counterfactual generator for language models. They
demonstrate empirically that the augmentation of training data through
\emph{Polyjuice} counterfactuals improves robustness in a number of NLP
tasks. Balashankar et al.
(\citeproc{ref-balashankar2023improving}{2023}) similarly use
\emph{Polyjuice} to augment NLP datasets through diverse counterfactuals
and show that classifier robustness improves by up to 20\%. Finally, Luu
and Inoue (\citeproc{ref-luu2023counterfactual}{2023}) introduce
Counterfactual Adversarial Training (CAT), which also aims at improving
generalization and robustness of language models through a three-step
procedure. First, the authors identify training samples that are subject
to high predictive uncertainty. Second, they generate counterfactual
explanations for those samples. Finally, they fine-tune the given
language model on the augmented dataset that includes the generated
counterfactuals.

@@

Two recent works are closely related to ours in that they use
counterfactuals during training with the explicit goal of affecting
certain properties of the post-hoc counterfactual explanations. Firstly,
Ross, Lakkaraju, and Bastani (\citeproc{ref-ross2021learning}{2024})
propose a way to train models that guarantee individual recourse to some
positive target class with high probability. Their approach builds on
adversarial training by explicitly inducing susceptibility to targeted
adversarial examples for the positive class. Additionally, the proposed
method allows for imposing a set of actionability constraints ex-ante.
For example, users can specify that certain features (e.g., \emph{age},
\emph{gender}) are immutable. Secondly, Guo, Nguyen, and Yadav
(\citeproc{ref-guo2023counternet}{2023}) are the first to propose an
end-to-end training pipeline that includes counterfactual explanations
as part of the training procedure. In particular, they propose a
specific network architecture that includes a predictor and CE generator
network, where the parameters of the CE generator network are learnable.
Counterfactuals are generated during each training iteration and fed
back to the predictor network. In contrast to Guo, Nguyen, and Yadav
(\citeproc{ref-guo2023counternet}{2023}), we impose no restrictions on
the neural network architecture at all.

@@

Grathwohl et al. (\citeproc{ref-grathwohl2020your}{2020}) observe that
any classifier can be re-interpreted as a joint energy-based model (JEM)
that learns to discriminate output classes conditional on the observed
(training) samples from \(p(\mathbf{x})\) and the generated samples from
\(p_\theta(\mathbf{x})\). The authors show that JEMs can be trained to
perform well at both tasks by directly maximizing the joint
log-likelihood factorized as
\(\log p_\theta(\mathbf{x},\mathbf{y})=\log p_\theta(\mathbf{y}|\mathbf{x}) + \log p_\theta(\mathbf{x})\).
The first term can be optimized using conventional cross-entropy as in
Equation~\ref{eq-obj}. Then, to optimize \(\log p_\theta(\mathbf{x})\)
Grathwohl et al. (\citeproc{ref-grathwohl2020your}{2020}) minimize the
contrastive divergence between these observed samples from
\(p(\mathbf{x})\) and generated samples from \(p_\theta(\mathbf{x})\).

@@

\subsubsection{Impact of hyperparameter
settings}\label{sec-hyperparameters}

We test in-depth the impact of three types of hyperparameters; our
complete results are in the appendix.

\textbf{\emph{Hyperparameters of the CE generators.}} First, we observe
that CT is highly sensitive to hyperparameter settings but (a) there are
manageable patterns and (b) we can typically identify settings that
improve either plausibility or cost, and commonly both of them at the
same time. Second, we note that the choice of a CE generator has a major
impact on the results. For example, \emph{REVISE} tends to perform the
worst, most likely because it uses a surrogate VAE to generate
counterfactuals which impedes faithfulness
(\citeproc{ref-altmeyer2024faithful}{Altmeyer et al. 2024}). Third,
increasing \(T\), the maximum number of steps, generally yields better
outcomes because more CEs can mature in each training epoch. Fourth, the
impact of \(\tau\), the required decision threshold is more difficult to
predict. On ``harder'' datasets it may be difficult to satisfy high
\(\tau\) for any given sample (i.e., also factuals) and so increasing
this threshold does not seem to correlate with better outcomes. In fact,
we have generally found that a choice of \(\tau=0.5\) leads to optimal
results because it is associated with high proportions of mature
counterfactuals.

\textbf{\emph{Hyperparameters for penalties.}} We find that the strength
of the energy regularization, \(\lambda_{\text{reg}}\) is highly
impactful; energy must be sufficiently regularized to avoid poor
performance in terms of decreased plausibility and increased costs. The
sensitivity with respect to \(\lambda_{\text{div}}\) and
\(\lambda_{\text{adv}}\) is much less evident. While high values of
\(\lambda_{\text{reg}}\) may increase the variability in outcomes when
combined with high values of \(\lambda_{\text{div}}\) or
\(\lambda_{\text{adv}}\), this effect is not very pronounced.

\textbf{\emph{Other hyperparameters.}} We observe that the effectiveness
and stability of CT is positively associated with the number of
counterfactuals generated during each training epoch. We also confirm
that a higher number of training epochs is beneficial. Interestingly, we
observed desired improvements in explainability when CT was combined
with conventional training and applied only for the final 50\% of epochs
of the complete training process. Put differently, CT may be a way to
improve the explainability of models in a fine-tuning manner.

@@

We first address the direct extensions of CT in
Section~\ref{sec-approach}. Then, we look at its limitations and
challenges in Section~\ref{sec-limitations}.

\subsection{Future Research}\label{sec-approach}

\textbf{\emph{CT is defined only for classification settings.}} Our
formulation relies on the distinction between non-target class(es)
\(y^{-}\) and target class(es) \(y^{+}\) to generate counterfactuals
through Equation~\ref{eq-obj}. While \(y^{-}\) and \(y^{+}\) can be
arbitrarily defined, CT requires the output space \(\mathcal{Y}\) to be
discrete. Thus, it does not apply to ML tasks where the change in
outcome cannot be readily quantified. Focus on classification models is
a common restriction in research on CEs and AR. Other settings have
attracted some interest (e.g., regression in
(\citeproc{ref-spooner2021counterfactual}{Spooner et al. 2021};
\citeproc{ref-zhao2023counterfactual}{Zhao, Broelemann, and Kasneci
2023})), but there is little consensus how to robustly extend the notion
of counterfactuals.

\textbf{\emph{CT is subject to training instabilities.}} JEMs are
susceptible to instabilities during training
(\citeproc{ref-grathwohl2020your}{Grathwohl et al. 2020}) and even
though we depart from the SGLD-based sampling, we still encounter major
variability in the outcomes. CT is exposed to two potential sources of
instabilities: (1) the energy-based contrastive divergence term in
Equation~\ref{eq-div}, and (2) the underlying counterfactual explainers.
Still, we find that training instabilities can be successfully mitigated
by regularizing energy (\(\lambda_{\text{reg}}\)), generating
sufficiently many counterfactuals during each training epoch, and
including only mature counterfactuals for contrastive divergence.

\textbf{\emph{CT is sensitive to hyperparameter selection.}} Our method
benefits from the tuning of certain key hyperparameters (see
Section~\ref{sec-hyperparameters}). In this work, we have relied
exclusively on grid search for this task. Future work on CT could
benefit from investigating more sophisticated approaches towards
hyperparameter tuning. Notably, CT is iterative which makes a variety of
methods applicable, including Bayesian (e.g.,
\citeproc{ref-snoek2012practical}{Snoek, Larochelle, and Adams 2012}) or
gradient-based (e.g., \citeproc{ref-franceschi2017forward}{Franceschi et
al. 2017}) optimization.

\subsection{Current Limitations}\label{sec-limitations}

\textbf{\emph{CT increases the training time of models.}} CT can be more
time-consuming than conventional training regimes. While higher numbers
of CEs per iteration positively impact the quality of solutions, they
also increase the amount of computations. Relatively small grids with
270 settings can take almost four hours for more demanding datasets on a
high-performance computing cluster with 34 2GB CPUs.\footnote{See
  supplementary appendix for computational details.} Three factors
attenuate this effect. First, CT amortizes the cost of CEs for the
training samples. Second, we find that it can retain its value when used
as a ``fine-tuning'' technique for conventionally-trained models. Third,
it yields itself to parallel execution, which we have leveraged for our
own experiments.

\textbf{\emph{Immutable features may have proxies.}} We propose an
approach to protect immutable features and thus increase the
actionability of the generated CEs. However, it requires that model
owners define the mutability constraints for (all) features considered
by the model. Even if all immutable features are protected, there may
exist proxies that are mutable (and hence should not be protected) but
preserve enough information about the principals to hinder the
protections. Delineating actionability is a major undecided challenge in
the AR literature (see, e.g.,
\citeproc{ref-venkatasubramanian2020philosophical}{Venkatasubramanian
and Alfano 2020}) impacting the capacity of CT to increase the
explainability of the model.

\textbf{\emph{Interventions on features may impact fairness.}} We
provide a tool that allows practitioners to modify the sensitivity of a
model with respect to certain features, which may have implication for
the fair and equitable treatment of decision subjects. As protecting a
set of features leads the model to assign higher relative importance to
unprotected features, model owners could misuse our solution by
enforcing explanations based on features that are more difficult to
modify by some (group of) individuals. For example, consider the Adult
dataset used in our experiments, where \emph{workclass} or
\emph{education} may be more difficult to change for underpriviledged
groups. When applied irresponsibly, CT could result in an unfairly
assigned burden of recourse (e.g.,
\citeproc{ref-sharma2020certifai}{Sharma, Henderson, and Ghosh 2020}),
threatening the equality of opportunity in the system
(\citeproc{ref-bell2024fairness}{Bell et al. 2024}). Still, these
phenomena are not specific to CT.

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Package Version (Reproducibility)}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-warning-color-frame, colbacktitle=quarto-callout-warning-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-tune-train}: Training Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-tune_lr-train}: Training Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, opacitybacktitle=0.6, toprule=.15mm, rightrule=.15mm, colback=white, arc=.35mm, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, coltitle=black, opacityback=0, titlerule=0mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, breakable]

>>>>

In the natural language processing (NLP) domain, CEs have also been used
to improve models through data augmentation. Wu et al.
(\citeproc{ref-wu2021polyjuice}{2021}) propose \emph{Polyjuice}, a
general-purpose counterfactual generator for language models. The
authors empirically demonstrate that the augmentation of training data
with their method improves robustness in a number of NLP tasks.
Balashankar et al. (\citeproc{ref-balashankar2023improving}{2023})
similarly use \emph{Polyjuice} to augment NLP datasets through diverse
counterfactuals and show that classifier robustness improves by up to
20\%. Finally, Luu and Inoue
(\citeproc{ref-luu2023counterfactual}{2023}) introduce Counterfactual
Adversarial Training (CAT), which also aims at improving generalization
and robustness of language models through a three-step procedure: the
authors identify training samples that are subject to high predictive
uncertainty, generate CEs for those samples, and then fine-tune the
language model on a dataset augmented with the CEs.

@@

Two recent works are closely related to ours in that they use
counterfactuals during training with the explicit goal of affecting
certain properties of the post-hoc counterfactual explanations. Firstly,
Ross, Lakkaraju, and Bastani (\citeproc{ref-ross2021learning}{2024})
propose a way to train models that guarantee individual recourse to some
positive target class with high probability. Their approach builds on
adversarial training by explicitly inducing susceptibility to targeted
adversarial examples for the positive class. Additionally, the proposed
method allows for imposing a set of actionability constraints ex-ante.
For example, users can specify that certain features are immutable.
Secondly, Guo, Nguyen, and Yadav
(\citeproc{ref-guo2023counternet}{2023}) are the first to propose an
end-to-end training pipeline that includes CEs as part of the training
procedure. In particular, they propose a specific network architecture
that includes a predictor and CE generator network, where the parameters
of the CE generator network are learnable. Counterfactuals are generated
during each training iteration and fed back to the predictor network. In
contrast to Guo, Nguyen, and Yadav
(\citeproc{ref-guo2023counternet}{2023}), we impose no restrictions on
the ANN architecture at all.

@@

As observed by Grathwohl et al.
(\citeproc{ref-grathwohl2020your}{2020}), any classifier can be
re-interpreted as a joint energy-based model (JEM) that learns to
discriminate output classes conditional on the observed (training)
samples from \(p(\mathbf{x})\) and the generated samples from
\(p_\theta(\mathbf{x})\). The authors show that JEMs can be trained to
perform well at both tasks by directly maximizing the joint
log-likelihood factorized as
\(\log p_\theta(\mathbf{x},\mathbf{y})=\log p_\theta(\mathbf{y}|\mathbf{x}) + \log p_\theta(\mathbf{x})\).
The first term can be optimized using conventional cross-entropy as in
Equation~\ref{eq-obj}. Then, to optimize \(\log p_\theta(\mathbf{x})\)
Grathwohl et al. (\citeproc{ref-grathwohl2020your}{2020}) minimize the
contrastive divergence between these observed samples from
\(p(\mathbf{x})\) and generated samples from \(p_\theta(\mathbf{x})\).

@@

\subsubsection{Impact of hyperparameter
settings.}\label{sec-hyperparameters}

We test the impact of three types of hyperparameters; our complete
results are in the supplementary appendix.\\
\textbf{\emph{Hyperparameters of the CE generators.}} First, we observe
that CT is highly sensitive to hyperparameter settings but (a) there are
manageable patterns and (b) we can typically identify settings that
improve either plausibility or cost, and commonly both of them at the
same time. Second, we note that the choice of a CE generator has a major
impact on the results. For example, \emph{REVISE} tends to perform the
worst, most likely because it uses a surrogate VAE to generate
counterfactuals which impedes faithfulness
(\citeproc{ref-altmeyer2024faithful}{Altmeyer et al. 2024}). Third,
increasing \(T\), the maximum number of steps, generally yields better
outcomes because more CEs can mature in each training epoch. Fourth, the
impact of \(\tau\), the required decision threshold is more difficult to
predict. On ``harder'' datasets it may be difficult to satisfy high
\(\tau\) for any given sample (i.e., also factuals) and so increasing
this threshold does not seem to correlate with better outcomes. In fact,
we have generally found that a choice of \(\tau=0.5\) leads to optimal
results because it is associated with high proportions of mature
counterfactuals.\\
\textbf{\emph{Hyperparameters for penalties.}} We find that the strength
of the energy regularization, \(\lambda_{\text{reg}}\) is highly
impactful; energy must be sufficiently regularized to avoid poor
performance in terms of decreased plausibility and increased costs. The
sensitivity with respect to \(\lambda_{\text{div}}\) and
\(\lambda_{\text{adv}}\) is much less evident. While high values of
\(\lambda_{\text{reg}}\) may increase the variability in outcomes when
combined with high values of \(\lambda_{\text{div}}\) or
\(\lambda_{\text{adv}}\), this effect is not very pronounced.\\
\textbf{\emph{Other hyperparameters.}} We observe that the effectiveness
and stability of CT is positively associated with the number of
counterfactuals generated during each training epoch. We also confirm
that a higher number of training epochs is beneficial. Interestingly, we
observed desired improvements in explainability when CT was combined
with conventional training and applied only for the final 50\% of epochs
of the complete training process. Put differently, CT may be a way to
improve the explainability of models in a fine-tuning manner.

@@

As our results indicate, counterfactual training produces models that
are more explainable. However, our approach is not without
limitations.\\
\textbf{\emph{CT increases the training time of models.}} CT can be more
time-consuming than conventional training regimes. While higher numbers
of CEs per iteration positively impact the quality of solutions, they
also increase the amount of computations. Relatively small grids with
270 settings can take almost four hours for more demanding datasets on a
high-performance computing cluster with 34 2GB CPUs.\footnote{See
  supplementary appendix for computational details.} Three factors
attenuate this effect. First, CT amortizes the cost of CEs for the
training samples. Second, we find that it can retain its value when used
as a ``fine-tuning'' technique for conventionally-trained models. Third,
it yields itself to parallel execution, which we have leveraged for our
own experiments.\\
\textbf{\emph{Immutable features may have proxies.}} We propose an
approach to protect immutable features and thus increase the
actionability of the generated CEs. However, it requires that model
owners define the mutability constraints for (all) features considered
by the model. Even if all immutable features are protected, there may
exist proxies that are mutable (and hence should not be protected) but
preserve enough information about the principals to hinder the
protections. Delineating actionability is a major undecided challenge in
the AR literature (see, e.g.,
\citeproc{ref-venkatasubramanian2020philosophical}{Venkatasubramanian
and Alfano 2020}) impacting the capacity of CT to fulfill its intended
goal.\\
\textbf{\emph{Interventions on features may impact fairness.}} We
provide a tool that allows practitioners to modify the sensitivity of a
model with respect to certain features, which may have implication for
the fair and equitable treatment of decision subjects. As protecting a
set of features leads the model to assign higher relative importance to
unprotected features, model owners could misuse our solution by
enforcing explanations based on features that are more difficult to
modify by some (group of) individuals. For example, consider the Adult
dataset used in our experiments, where \emph{workclass} or
\emph{education} may be more difficult to change for underpriviledged
groups. When applied irresponsibly, CT could result in an unfairly
assigned burden of recourse (e.g.,
\citeproc{ref-sharma2020certifai}{Sharma, Henderson, and Ghosh 2020}),
threatening the equality of opportunity in the system
(\citeproc{ref-bell2024fairness}{Bell et al. 2024}). Still, these
phenomena are not specific to CT.

We also highlight several interesting directions for future research.\\
\textbf{\emph{Extending CT beyond classification settings.}} Our
formulation relies on the distinction between non-target class(es)
\(y^{-}\) and target class(es) \(y^{+}\) to generate counterfactuals
through Equation~\ref{eq-obj}. While \(y^{-}\) and \(y^{+}\) can be
arbitrarily defined, CT requires the output space \(\mathcal{Y}\) to be
discrete. Thus, it does not apply to ML tasks where the change in
outcome cannot be readily quantified. Focus on classification models is
a common restriction in research on CEs and AR. Other settings have
attracted some interest (e.g., regression in
(\citeproc{ref-spooner2021counterfactual}{Spooner et al. 2021};
\citeproc{ref-zhao2023counterfactual}{Zhao, Broelemann, and Kasneci
2023})), but there is little consensus how to robustly extend the notion
of CEs.\\
\textbf{\emph{Addressing the training instabilities.}} JEMs are
susceptible to instabilities during training
(\citeproc{ref-grathwohl2020your}{Grathwohl et al. 2020}) and even
though we depart from the SGLD-based sampling, we still encounter major
variability in the outcomes. CT is exposed to two potential sources of
instabilities: (1) the energy-based contrastive divergence term in
Equation~\ref{eq-div}, and (2) the underlying counterfactual explainers.
Still, we find that training instabilities can be successfully mitigated
by regularizing energy (\(\lambda_{\text{reg}}\)), generating
sufficiently many counterfactuals during each training epoch, and
including only mature counterfactuals for contrastive divergence.\\
\textbf{\emph{Improving hyperparameter selection procedures.}} Our
method benefits from the tuning of certain key hyperparameters (see
Section~\ref{sec-hyperparameters}). In this work, we have relied
exclusively on grid search for this task. Future work on CT could
benefit from investigating more sophisticated approaches towards
hyperparameter tuning. Notably, CT is iterative which makes a variety of
methods applicable, including Bayesian (e.g.,
\citeproc{ref-snoek2012practical}{Snoek, Larochelle, and Adams 2012}) or
gradient-based (e.g., \citeproc{ref-franceschi2017forward}{Franceschi et
al. 2017}) optimization.

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-train-final-run-train}: Training Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-warning-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-warning-color-frame, rightrule=.15mm, coltitle=black, title={Package Version (Reproducibility)}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-tune-train}: Training Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-tune_lr-train}: Training Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, left=2mm, leftrule=.75mm, opacityback=0, colback=white, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, toprule=.15mm, bottomrule=.15mm, arc=.35mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, coltitle=black, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, titlerule=0mm, bottomtitle=1mm, opacitybacktitle=0.6]
